Countermeasures against co-location attempts in the cloud

### 2015-02-25 paper.tex
style fixes

\begin{abstract}
Recent research has demonstrated that cloud services such as Amazon AWS do not provide perfect isolation --- that there
  are side channels between virtual machines that reside on the same host.
In particular, it is possible, under some circumstances, to use cache timing information to perform a full AES key
  recovery against a VM sharing the same cache.

@@

\begin{itemize}
	\item Amazon's EC2 service is very popular and used for by variety of customers, some with sensitive data
	\item This makes VMs on this service a worthwhile target
	\item Ristenpart et. al have demonstrated that it is possible to create a VM co-resident with a target instance and
	that existing side-channel attacks can be employed against co-resident instances on the cloud
	\item We would like to focus on a method to obscure the algorithm by which instances are placed, which would make it
	significantly harder to achieve co-location
	\item Alternatively, we could focus on a method which prevents the simple network-based checks used to determine if two instances are co-located.

\end{itemize}

>>>>

\begin{abstract}
Recent research has demonstrated that cloud services such as Amazon AWS do not provide perfect isolation~--- that there
  are side channels between virtual machines that reside on the same host.
In particular, it is possible, under some circumstances, to use cache timing information to perform a full AES key
  recovery against a VM sharing the same cache.

@@

\begin{itemize}
  \item Amazon's EC2 service is very popular and used for by variety of customers, some with sensitive data.
  \item This makes VMs on this service a worthwhile target.
  \item Ristenpart et. al have demonstrated that it is possible to create a VM co-resident with a target instance and
    that existing side-channel attacks can be employed against co-resident instances on the cloud.
  \item We would like to focus on a method to obscure the algorithm by which instances are placed, which would make it
    significantly harder to achieve co-location.
  \item Alternatively, we could focus on a method which prevents the simple network-based checks used to determine if
    two instances are co-located.
\end{itemize}
